Summarize twas: chr17 to 22

### 2020-09-20 analysis/simulation-multi-ukbchr17to22-gtex.adipose_susieprior.Rmd
susie cali truth

>>>>

# Simulation 1-x, test true prior

```{r output-t dir}
simdatadir <- "~/causalTWAS/simulations/simulation_ashtest_20200721/"
outputdir <- "~/causalTWAS/simulations/simulation_ashtest_20200721/"
susiedir <- "/home/simingz/causalTWAS/simulations/simulation_susietest_20200721/20200721-1-fixprior_rpip0.5/"
```

We run 50 simulations and run susie using the true parameter (gene and snp pi1) as prior. We run susie for regions with regional sum of pip from mr.ash2s for both genes and snps > 0.5. run susie with L=1.

* The true parameters we used to simulate data: 
```{r  true par-t}
par <- read.table(paste0(susiedir, "20200721-1-fixedprior_1.txt"), header = T)
t(par[,2, drop = F])
```

## Use truth as prior

* The prior used is: 
```{r  par1-t}
par <- read.table(paste0(susiedir, "20200721-1-fixedprior_2.txt"), header = T)
t(par[c(1,3),1, drop = F])
```
* susie results: 
```{r cali 1-t, fig.height=6, fig.width=14}
pipfs <- Sys.glob(paste0(susiedir,"20200721-1-*.fixedprior2.L1.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))
par(mfrow=c(1,2))
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```
